A spiral galaxy's mass distribution uncovered through lensing and dynamics

### 2015-11-16 docs/results_lensing_v3.01.tex
More corrections; abstract is now 250 words long; edited introduction.

\paragraph{Image positions.} We determine the positions of the lensing images by first subtracting a smooth model for the galaxy's surface brightness from the original image. As models we use MGE fits and IRAF \emph{ellipse} fits  (see Sections \ref{sec:MGE_theo} and \ref{sec:MGE_results})  to the galaxy in each the F450W and F814W filter. (For example the MGE we use for F814W is the MGE given in Table \ref{tab:MGEF814W} convolved with the PSF in Table \ref{tab:PSFMGEF814W}.) The lensing images become then visible in the residuals (see Figure \ref{fig:lens_just_imgpos}), in which we smooth out noise smaller than the PSF. Because the lensing images are extended, we use the position of the brightest pixel in each of the images. We also use the F450W-MGE subtracted residuals from \citet{SWELLSIII}. The lensing positions as determined from the latter are given in Table \ref{tab:lenspos}. The scatter of lensing positions as determined from subtracting different surface brightness models from the galaxy in different filters gives an error of $\pm 1$ pixel on the image positions. We find slightly different positions for the peak of the surface brightness in the different filters and apply correspondingly an error of one diagonal pixel to the brightness peak in the F450W image which we use as center of the galaxy.
\\Eight image position coordinates allow us to fit a lens mass model with only $<8$ free parameters. We therefore do not fit Fourier components $(a_k,b_k)$ with $k > 3$.
\\Even though the constraints from the image positions on $\alpha$ is very weak, we were however able to show that the image positions in Table \ref{tab:lenspos} are consistent with a model with flat rotation curve. In the following we therefore set $\alpha=1$.

@@

\paragraph{Best fit lens model.} The best fit lens model for the image positions in Table \ref{tab:lenspos} is given in the first column of Table \ref{tab:bestfitlensmodel}. Figure \ref{fig:lensbestfiteinsteincurves} shows the corresponding critical curve, caustic and Einstein radius, and the best fit source position. In this case, where $\alpha=1$, the critical curve is also an equidensity contour of the galaxy model \citep{EvansWitt}, which appears to have an elliptical mass distribution. This cricital curve is called \emph{tangential}, because of the tangential orientation of the images close to it. The source is located close to a cusp of the diamond-shaped caustic: a lensing configuration for which we indeed expect four images. This is a good indication that indeed all four images are indeed lensing images of the same object. Figure \ref{fig:lensbestfittimedelay} overplots the smoothed residuals from the F450W image subtracted by the IRAF \emph{ellipse} fit to the surface brightness with the contours of the best fit model's time delay surface. This demonstrates that, although we did not include any information about the shape of the lensing images in the fit, it is consistent with the predicted distortion for an extended source by the best fit lens model.
\\To estimate how the uncertainties in the determination of the image positions and galaxy center affect the results, we Monte Carlo sample random positions from a two-dimensional Normal distribution centered at the positions in Table \ref{tab:lenspos} and a standard deviation corresponding to the measurement error. A Gaussian fit to the resulting distributions of best fit values leads to the constraints on the shape parameters and Einstein quantities in the second column in Table \ref{tab:bestfitlensmodel}. We therefore constrain the Einstein radius to within 2\%, $R_\text{ein} = (0.91 \pm 0.02)''$ and the projected mass within the critical curve with a relative error of 4\%, $M_\text{crit} =(7.9\pm0.3)\cdot 10^{10} M_\odot$. Our measurement of $R_\text{ein}$ is consistent with that from \citet{SWELLSIII}, $R_\text{ein,SWELLS} = (0.96 \pm 0.04)''$ (which used a singular isothermal ellipsoid as lens mass model and the intermediate-axis convention of the critical curve as the Einstein radius). The relative difference between our critical mass and that of \citet{SWELLSIII}, $M_\text{crit,SWELLS} =(8.86\pm0.61)\cdot 10^{10} M_\odot$, is 13\%.

@@

\begin{figure*}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/lens_einstein.ps}
  \caption{Best fit critical curve, Einstein radius, caustic, source position.}
  \label{fig:lensbestfiteinsteincurves}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/lens_timedelay.ps}
  \caption{Time delay surface.}
  \label{fig:lensbestfittimedelay}
\end{subfigure}
\caption{Best fit lens model in Table \ref{tab:bestfitlensmodel} found from the image positions. In the background we show the central region of J1331 in the F450W filter, subtracted by an IRAF \emph{ellipse} model of the F450W surface brightness and smoothed by boxcar smoothing of the order of the PSF size. The four bluish lensing images are clearly visible and we mark the brightness peaks in Table \ref{tab:lenspos} as well as the galaxy center (G) as red dots. The Einstein radius of the best fit lens model is shown as a red dotted circle. \emph{Panel (a)} Besides the image positions and Einstein radius, the critical curve (red solid line) is shown in the lens plane. The caustic (green solid line) corresponding to the critical curve and best fit source position (green dot), which are both located in the source plane, are shown as well. For $\alpha=1$ (which we assumed for our lens model) the critical curve is a contour of constant surface density of the mass model. \emph{Panel (b)} The yellow lines show (arbitrary) contours of the time delay surface given by Equation \ref{eq:timedelay} of the best fit lens model. Not only the position of the extrema, but also their shape is consistent with the observed, extended images, even though we did not use information about the image shape in the analysis. The other two right blobs (north east of A, south east of B) might be star forming regions of the background galaxy as well. \Wilma{[TO DO: Add A, B, C, D in the figure to make clear which image is which.]}}
\label{fig:???}
\end{figure*}

@@

\paragraph{Comparison with light distribution.} The surface mass distribution as predicted by the best fit model in Table \ref{tab:bestfitlensmodel} is shown in Figure \ref{fig:lenscomparemass}. We introduced random noise according to the uncertainties in the Fourier shape parameters to create a mock observation that visualizes the effect of the measurement errors. From the mock image's second moment we find an average axis ratio for the lens mass model of $q_\text{lens} \simeq 0.695$, which is consistent with the one found by \citet{SWELLSIII}, $q_\text{lens,SWELLSIII} = 0.67 \pm 0.09$, while the light's average axis ratio in Table \ref{tab:galaxyparameters} is $q' = 0.598$.
\\To estimate the total mass-to-light ratio within the Einstein radius $\Upsilon_\text{I,tot}^\text{ein} = M_\text{ein} / L_\text{I,ein}$, we first integrate the MGE in Table \ref{tab:MGEF814W} to get the total luminosity within the Einstein radius $L_\text{I,ein}$. $L_\text{I,ein}$ and $\Upsilon_\text{I,tot}^\text{ein}$ are given in Table \ref{tab:einsteinML}. $\Upsilon_\text{I,tot}^\text{ein} \sim 5.6$ is consistent or slightly larger than the stellar mass-to-light ratio assuming a Salpeter Initial Mass Function $\Upsilon_\text{I,*}^\text{sal} = 4.7 \pm 1.2$ according to \citet{SWELLSI} and Table \ref{tab:previousresults} (see also discussion in Section \ref{sec:MLdiscussion}). We use $\Upsilon_\text{I,tot}^\text{ein}$ to transform the observed surface brightness in the F814W filter into a surface mass density to compare it to the lensing mass distribution (Figure \ref{fig:lenscomparelight}). Figure \ref{fig:lenscompareboth} then compares equidensity contours at the same values of both the predicted lens mass distribution and the observed surface brightness times $\Upsilon_\text{I,tot}^\text{ein}$.
\\Figure \ref{fig:lenslightcompareALL} leads to the following three findings: (1)The mass predicted from lensing and the observed light distribution are oriented in the same direction (i.e. have the same position angle). (2) Within and around the Einstein radius, mass and light distribution have a similar elliptical shape, while further out the mass distribution is slightly rounder. (3) The light distribution drops faster than the mass with increasing radius. Astrophysical reasons for the differences in observed light and measured mass distribution could be, e.g. an apparent change of shape due to dust extinction, a strongly changing $\Upsilon_\text{I,*}$, or the stellar component of the galaxy could be superimposed by a more roundish dark matter component.  We have to note however that the mass distribution is only constraint around the Einstein radius and otherwise an extrapolation.

@@

\begin{table*}
\centering
\caption{Total I-band (F814W) luminosity inside the Einstein radius $R_\text{ein}$, found from integrating the MGE in Table \ref{tab:MGEF814W} and corresponding total mass-to-light ratio $\Upsilon_\text{I,tot}^\text{ein}$ using the Einstein mass $M_\text{ein}$. $R_\text{ein}$ and $M_\text{ein}$ are given in Table \ref{tab:bestfitlensmodel}.}
\begin{tabular}{cc}
\hline
Total I-band luminosity within $R_\text{ein}$ & Mass-to-light ratio within $R_\text{ein}$\\
 $L_\text{I,ein}$ [$10^{10} L_\odot$] & $\Upsilon_\text{I,tot}^\text{ein} = M_\text{ein} / L_\text{I,ein}$ [$\Upsilon_{\text{I},\odot}$]\\\hline
1.40 & 5.56\\\hline
\end{tabular}  
\label{tab:einsteinML} 
\end{table*}

>>>>

\paragraph{Image positions.} We determine the positions of the lensing images by first subtracting a smooth model for the galaxy's surface brightness from the original image. As models we use MGE fits and IRAF \emph{ellipse} fits  (see Sections \ref{sec:MGE_theo} and \ref{sec:MGE_results})  to the galaxy in each the F450W and F814W filter. (For example the MGE we use for F814W is the MGE given in Table \ref{tab:MGEF814W} convolved with the PSF in Table \ref{tab:PSFMGEF814W}.) The lensing images become then visible in the residuals (see Figure \ref{fig:lens_just_imgpos}), in which we smooth out noise smaller than the PSF. Because the lensing images are extended, we use the position of the brightest pixel in each of the images. We also use the F450W-MGE subtracted residuals from \citet{SWELLSIII}. The lensing positions as determined from the latter are given in Table \ref{tab:lenspos}. The scatter of lensing positions as determined from subtracting different surface brightness models from the galaxy in different filters gives an error of $\pm 1$ pixel on the image positions. We find slightly different positions for the peak of the surface brightness in the different filters and apply correspondingly an error of one diagonal pixel to the brightness peak in the F450W image which we use as center of the galaxy.

Eight image position coordinates allow us to fit a lens mass model with only $<8$ free parameters. We therefore do not fit Fourier components $(a_k,b_k)$ with $k > 3$.

Even though the constraints from the image positions on $\alpha$ is very weak, we were however able to show that the image positions in Table \ref{tab:lenspos} are consistent with a model with flat rotation curve. In the following we therefore set $\alpha=1$.

@@

\paragraph{Best fit lens model.} The best fit lens model for the image positions in Table \ref{tab:lenspos} is given in the first column of Table \ref{tab:bestfitlensmodel}. Figure \ref{fig:lensbestfiteinsteincurves} shows the corresponding critical curve, caustic and Einstein radius, and the best fit source position. In this case, where $\alpha=1$, the critical curve is also an equidensity contour of the galaxy model \citep{EvansWitt}, which appears to have an elliptical mass distribution. This cricital curve is called \emph{tangential}, because of the tangential orientation of the images close to it. The source is located close to a cusp of the diamond-shaped caustic: a lensing configuration for which we indeed expect four images. This is a good indication that indeed all four images are indeed lensing images of the same object. Figure \ref{fig:lensbestfittimedelay} overplots the smoothed residuals from the F450W image subtracted by the IRAF \emph{ellipse} fit to the surface brightness with the contours of the best fit model's time delay surface. This demonstrates that, although we did not include any information about the shape of the lensing images in the fit, it is consistent with the predicted distortion for an extended source by the best fit lens model.

To estimate how the uncertainties in the determination of the image positions and galaxy center affect the results, we Monte Carlo sample random positions from a two-dimensional Normal distribution centered at the positions in Table \ref{tab:lenspos} and a standard deviation corresponding to the measurement error. A Gaussian fit to the resulting distributions of best fit values leads to the constraints on the shape parameters and Einstein quantities in the second column in Table \ref{tab:bestfitlensmodel}. We therefore constrain the Einstein radius to within 2\%, $R_\text{ein} = (0.91 \pm 0.02)''$ and the projected mass within the critical curve with a relative error of 4\%, $M_\text{crit} =(7.9\pm0.3)\cdot 10^{10} M_\odot$. Our measurement of $R_\text{ein}$ is consistent with that from \citet{SWELLSIII}, $R_\text{ein,SWELLS} = (0.96 \pm 0.04)''$ (which used a singular isothermal ellipsoid as lens mass model and the intermediate-axis convention of the critical curve as the Einstein radius). The relative difference between our critical mass and that of \citet{SWELLSIII}, $M_\text{crit,SWELLS} =(8.86\pm0.61)\cdot 10^{10} M_\odot$, is 13\%.

@@

\begin{figure*}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/lens_einstein.ps}
  \caption{Best fit critical curve, Einstein radius, caustic, source position.}
  \label{fig:lensbestfiteinsteincurves}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/lens_timedelay.ps}
  \caption{Time delay surface.}
  \label{fig:lensbestfittimedelay}
\end{subfigure}
\caption{Best fit lens model in Table \ref{tab:bestfitlensmodel} found from the image positions. In the background we show the central region of J1331 in the F450W filter, subtracted by an IRAF \emph{ellipse} model of the F450W surface brightness and smoothed by boxcar smoothing of the order of the PSF size. The four bluish lensing images are clearly visible and we mark the brightness peaks in Table \ref{tab:lenspos} as well as the galaxy center (G) as red dots. The Einstein radius of the best fit lens model is shown as a red dotted circle. \emph{Panel (a)} Besides the image positions and Einstein radius, the critical curve (red solid line) is shown in the lens plane. The caustic (green solid line) corresponding to the critical curve and best fit source position (green dot), which are both located in the source plane, are shown as well. For $\alpha=1$ (which we assumed for our lens model) the critical curve is a contour of constant surface density of the mass model. \emph{Panel (b)} The yellow lines show (arbitrary) contours of the time delay surface given by Equation \ref{eq:timedelay} of the best fit lens model. Not only the position of the extrema, but also their shape is consistent with the observed, extended images, even though we did not use information about the image shape in the analysis. The other two right blobs (north east of A, south east of B) might be star forming regions of the background galaxy as well. \Wilma{[TO DO: Add A, B, C, D in the figure to make clear which image is which.]} \Wilma{[TO DO: Combine in one figure. Make all lines except time delay surface very thick.]}}
\label{fig:???}
\end{figure*}

@@

\paragraph{Comparison with light distribution.} The surface mass distribution as predicted by the best fit lens model in Table \ref{tab:bestfitlensmodel} is shown in Figure \ref{fig:lenscomparemass}. We introduced random noise according to the uncertainties in the Fourier shape parameters to create a mock observation that visualizes the effect of the measurement errors. From the mock image's second moment we find an average axis ratio for the lens mass model of $q_\text{lens} \simeq 0.695$, which is consistent with the one found by \citet{SWELLSIII}, $q_\text{lens,SWELLSIII} = 0.67 \pm 0.09$, while the light's average axis ratio in Table \ref{tab:galaxyparameters} is $q' = 0.598$.

To estimate the total mass-to-light ratio within the Einstein radius $\Upsilon_\text{I,tot}^\text{ein} = M_\text{ein} / L_\text{I,ein}$, we first integrate the MGE in Table \ref{tab:MGEF814W} to get the total luminosity within the Einstein radius $L_\text{I,ein}$. $L_\text{I,ein}$ and $\Upsilon_\text{I,tot}^\text{ein}$ are given in Table \ref{tab:einsteinML} \Wilma{[TO DO: Put in text, no separate table.]}. $\Upsilon_\text{I,tot}^\text{ein} \sim 5.6$ is consistent or slightly larger than the stellar mass-to-light ratio assuming a Salpeter Initial Mass Function $\Upsilon_\text{I,*}^\text{sal} = 4.7 \pm 1.2$ according to \citet{SWELLSI} and Table \ref{tab:previousresults} (see also discussion in Section \ref{sec:MLdiscussion}). We use $\Upsilon_\text{I,tot}^\text{ein}$ to transform the observed surface brightness in the F814W filter into a surface mass density to compare it to the lensing mass distribution (Figure \ref{fig:lenscomparelight}). Figure \ref{fig:lenscompareboth} then compares equidensity contours at the same values of both the predicted lens mass distribution and the observed surface brightness times $\Upsilon_\text{I,tot}^\text{ein}$.

Figure \ref{fig:lenslightcompareALL} leads to the following three findings: (1)The mass predicted from lensing and the observed light distribution are oriented in the same direction (i.e. have the same position angle). (2) Within and around the Einstein radius, mass and light distribution have a similar elliptical shape, while further out the mass distribution is slightly rounder. (3) The light distribution drops faster than the mass with increasing radius (at least partly because of the assumption of a flat rotation curve). However, the mass distribution is only constraint around the Einstein radius and otherwise an extrapolation.

@@

\begin{table*}
\centering
\caption{Total I-band (F814W) luminosity inside the Einstein radius $R_\text{ein}$, found from integrating the MGE in Table \ref{tab:MGEF814W} and corresponding total mass-to-light ratio $\Upsilon_\text{I,tot}^\text{ein}$ using the Einstein mass $M_\text{ein}$. $R_\text{ein}$ and $M_\text{ein}$ are given in Table \ref{tab:bestfitlensmodel}. \Wilma{[TO DO: No separate table, put instead in text]}}
\begin{tabular}{cc}
\hline
Total I-band luminosity within $R_\text{ein}$ & Mass-to-light ratio within $R_\text{ein}$\\
 $L_\text{I,ein}$ [$10^{10} L_\odot$] & $\Upsilon_\text{I,tot}^\text{ein} = M_\text{ein} / L_\text{I,ein}$ [$\Upsilon_{\text{I},\odot}$]\\\hline
1.40 & 5.56\\\hline
\end{tabular}  
\label{tab:einsteinML} 
\end{table*}

### 2015-11-16 docs/results_photometry_v3.01.tex
More corrections; abstract is now 250 words long; edited introduction.

In this section we construct a model for the galaxy's intrinsic light distribution in terms of an MGE, which we will then compare in Section \ref{sec:results_lensing} to the mass distribution. The light model will also be the basis of the dynamical Jeans modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}.
\\To derive J1331's surface brightness distribution, we use the HST image in the F814W (I-band) filter, shown in Figure \ref{fig:F814W}. At longer wavelengths J1331's central old and smooth stellar component is more extended than in the F450W filter in Figure \ref{fig:F450W}, which is more sensitive to young clumpy star-forming regions. In the I-band the bulge is also much brighter than the bluish lens images and the imaging is less prone to extinction. The F814W image is therefore best suited for fitting a MGE.

@@

\paragraph{Transformation into physical units.} To transform the MGE in units of counts into physical units, we apply a simplified version of the procedure described in \citet{Holtzman}.
\\The scaling of the drizzled HST/WFC3 images is  $S = 0.05''/$pixel and the total exposure time $T = 1600$ sec. The total F814W luminosity in counts of each Gaussian of the MGE has a central surface brightness in counts per pixel of
\begin{equation*}
C_0\text{[counts/pixel]} = \frac{L[\text{counts}]}{2\pi \sigma[\text{pixel}]^2 q}.
\end{equation*}
This is then transformed into an I-band surface brightness via
\begin{equation}
\mu_{I,0} \simeq -2.5 \log_{10}\left( \frac{C_0\text{[counts/pixel]}}{T[\text{sec}] \cdot S[''/\text{pixel}]^2}\right) + Z + C + A_I, \label{eq:muI_}
\end{equation}
\Wilma{[TO DO: Make sure to use $\mu_{I,0}$ where applicable.]} where $Z\simeq21.62$ is a the zero-point from \citet{Holtzman}  (updated according to \citet{Dolphin,DolphinNew}) for the photometric system of the HST/WFPC2 camera and the F814W filter plus a correction for the difference in gain between calibration and observation. $C= 0.1$ corrects for the finite aperture of the WFPC2. And $A_I =0.015$ mag  is the extinction in the (Landolt) I-band towards J1331, according to the NASA/IPAC Extragalactic Database (NED)\footnote{The NASA/IPAC Extragalactic Database (NED, \url{https://ned.ipac.caltech.edu/}) is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration. The data for J1331 (SDSS J133140.33+362811.9) was retrieved in October 2013.}. The color-dependent correction between the F814W filter and the I-band of the UBVRI photometric system is  small \citep{Holtzman} and we neglect it therefore. The last step is to transform the surface brightness $\mu_i$ in mag to the I-band surface density of the Gaussian in $L_\odot$/pc$^2$ as
\begin{eqnarray*}
I_0[L_\odot \text{pc}^{-2}] = \left( 64800/\pi\right)^2 \left(1+z \right)^4 10^{0.4\left(M_{\odot,I}-\mu_{I,0} \right)},
\end{eqnarray*}
where the term with $z$ accounts for redshift dimming and $M_{\odot,I}=4.08$ mag is the sun's absolute I-band magnitude \citep{1998gaas.book.....B}. The luminosity $L_k$[counts] and the corresponding surface brightness density $I \equiv I_{0,k}[L_\odot \text{pc}^{-2}]$ of each Gaussian are given in Table \ref{fig:MGEinnerRegions}. \Wilma{[TO DO: I'm really confused about this. Check, that everything is correct and the naming of quantities, e.g. with or without subscripts of 0, is fine???]}

>>>>

In this section we construct a model for the galaxy's intrinsic light distribution in terms of an MGE, which we will then compare in Section \ref{sec:results_lensing} to the mass distribution. The light model will also be the basis of the dynamical Jeans modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}.

To derive J1331's surface brightness distribution, we use the HST image in the F814W (I-band) filter, shown in Figure \ref{fig:F814W}. At longer wavelengths J1331's central old and smooth stellar component is more extended than in the F450W filter in Figure \ref{fig:F450W}, which is more sensitive to young clumpy star-forming regions. In the I-band the bulge is also much brighter than the bluish lens images and the imaging is less prone to extinction. The F814W image is therefore best suited for fitting a MGE.

@@

\paragraph{Transformation into physical units.} To transform the MGE in units of counts into physical units, we apply a simplified version of the procedure described in \citet{Holtzman}.

The scaling of the drizzled HST/WFC3 images is  $S = 0.05''/$pixel and the total exposure time $T = 1600$ sec. The total F814W luminosity in counts of each Gaussian of the MGE has a central surface brightness in counts per pixel of
\begin{equation*}
C_0\text{[counts/pixel]} = \frac{L[\text{counts}]}{2\pi \sigma[\text{pixel}]^2 q}.
\end{equation*}
This is then transformed into an I-band surface brightness via
\begin{equation}
\mu_{I,0} \simeq -2.5 \log_{10}\left( \frac{C_0\text{[counts/pixel]}}{T[\text{sec}] \cdot S[''/\text{pixel}]^2}\right) + Z + C + A_I, \label{eq:muI_}
\end{equation}
\Wilma{[TO DO: Make sure to use $\mu_{I,0}$ where applicable.]} where $Z\simeq21.62$ is a the zero-point from \citet{Holtzman}  (updated according to \citet{Dolphin,DolphinNew}) for the photometric system of the HST/WFPC2 camera and the F814W filter plus a correction for the difference in gain between calibration and observation. $C= 0.1$ corrects for the finite aperture of the WFPC2. And $A_I =0.015$ mag  is the extinction in the (Landolt) I-band towards J1331, according to the NASA/IPAC Extragalactic Database (NED)\footnote{The NASA/IPAC Extragalactic Database (NED, \url{https://ned.ipac.caltech.edu/}) is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration. The data for J1331 (SDSS J133140.33+362811.9) was retrieved in October 2013.}. The color-dependent correction between the F814W filter and the I-band of the UBVRI photometric system is  small \citep{Holtzman} and we neglect it therefore. The last step is to transform the surface brightness $\mu_i$ in mag to the I-band surface density of the Gaussian in $L_\odot$/pc$^2$ as
\begin{eqnarray*}
I_0[L_\odot \text{pc}^{-2}] = \left( 64800/\pi\right)^2 \left(1+z \right)^4 10^{0.4\left(M_{\odot,I}-\mu_{I,0} \right)},
\end{eqnarray*}
where the term with $z$ accounts for redshift dimming and $M_{\odot,I}=4.08$ mag is the sun's absolute I-band magnitude \citep{1998gaas.book.....B}. The luminosity $L_k$[counts] and the corresponding surface brightness density $I \equiv I_{0,k}[L_\odot \text{pc}^{-2}]$ of each Gaussian are given in Table \ref{fig:MGEinnerRegions}. \Wilma{[TO DO: I'm really confused about this. Check, that everything is correct and the naming of quantities, e.g. with or without subscripts of 0, is fine???]}
